Dominance Regions for Rank Two Cluster Algebras

### 2022-04-04 dominance_regions.tex
Pictures

  When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
  We will therefore assume that $bc\ge4$.
  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$, $a_1,a_2\in\ZZ$, inside its \emph{dominance polygon} $\cP(\lambda)$.
  %In this case, we compute the possible transitions between any two pointed bases.
  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
  \begin{theorem}
    \label{th:dominance inequalities}
    The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
    {
      \everymath={\displaystyle}
      \def\arraystretch{2.8}
      \[
        \begin{array}{rcccl}
          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
          \\
          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
          \\
          0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
          \\
          \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
        \end{array}
      \]
    }
  \end{theorem}

  A number of bases for rank two cluster algebras with various defining properties have been defined.
  A natural starting basis is the so-called \emph{greedy basis} in which all $c^\lambda_{a_1,a_2}$ are non-negative and these coefficients are chosen to be minimal.
  It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications with the subalgebras of $\ZZ[x_1^{\pm1},x_2^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
  However, these bases depend on $k$ and the triangular basis is defined by a triangular transition with the stipulation that the basis does not depend on the choice of starting cluster.
  It would be useful to explicitly (or combinatorially) compute the transitions between these bases.
  However, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.

@@

\begin{figure}[h!]
  \centering
    \newcommand{\boundingrays}{
      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
      \draw [color=lightgray, thick, dashed] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
    }
  \begin{tikzpicture}[scale=.3]
    \begin{scope}[shift={(0,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l,\l) circle (6pt);
    \end{scope}
    \begin{scope}[shift={(13,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l *\b + \l, - \l) circle (6pt);
      \draw [very thick, join=round] (\l * \b + \l, -\l) -- (\l,-\l);
    \end{scope}
    \begin{scope}[shift={(26,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, \l) circle (6pt);
      \draw [very thick, join=round] (-\l, \l) -- (-\l,\l + \l*\c);
    \end{scope}
    \begin{scope}[shift={(39, 0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, -\l) circle (6pt);
      \draw [very thick, join=round] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
    \end{scope}
    \begin{scope}[shift={(0,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c -0.1; \y = -\l; }
      \fill (\x,\y) circle (6pt);
      \draw [very thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
    \end{scope}
    \begin{scope}[shift={(13,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c + 0.15; \y = -\l - 3*\l/10;}
      \fill (\x,\y) circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (0,0);
      \draw [very thick, dashed, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(26,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
      \fill (\x,\y) circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (0,0);
      \draw [very thick, dashed, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(39,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \c*\l/\b/1.03; \y = -\l; }
      \fill (\x , \y)  circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);
      \draw [very thick, dashed, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
    \end{scope}
  \end{tikzpicture}
\end{figure}

@@

  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
    For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
    \begin{enumerate}
      \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
      \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
      \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
      \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
      \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
      \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
      $$\aligned
      R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
      &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
      &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
      \endaligned
      $$
    \end{enumerate}
    Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$. 
  \end{theorem}
  \begin{figure}[h!]
    \centering
    \begin{tikzpicture}[scale=.7]
      %(1)
      \begin{scope}[shift={(-2.75, 5.5)}]
        \usetikzlibrary{patterns}
        \draw[-] (-0.5,0.25) -- (3,0.25);
        \draw[-] (0,-0.25) -- (0,3);
        \fill[white] (0,0.25) circle (2pt);
        \draw (0,0.25) circle (2pt);
        \draw (0,0.25) node[anchor=south west] {\tiny $O$};
        \fill (1.5,1.75) circle (2pt);
        \draw (1.5,1.75) node[anchor=east] {\tiny $B$};
        \draw (1.07,-.6) node[anchor=north] {\footnotesize (1) $a_1,a_2\le0$};
      \end{scope}
      %(2)
      \begin{scope}[shift={(2.75, 5.5)}]
        \usetikzlibrary{patterns}
        \draw[-] (-0.5,1.5) -- (3,1.5);
        \draw[-] (0,-0.25) -- (0,3);
        \fill[white] (0,1.5) circle (2pt);
        \draw (0,1.5) circle (2pt);
        \draw (0,1.5) node[anchor=south west] {\tiny $O$};
        \fill (2.25,0.5) circle (2pt);
        \draw (2.25,0.5) node[anchor=west] {\tiny$A$};
        \fill (0.75,0.5) circle (2pt);
        \draw (0.75,0.5) node[anchor=east] {\tiny$B$};
        \draw [thick] (0.75,0.5) -- (2.25,0.5);
        \draw (1.27,-.6) node[anchor=north] {\footnotesize (2) $a_1\le 0<a_2$};
      \end{scope}
      %(3)
      \begin{scope}[shift={(8.25,5.5)}]
        \usetikzlibrary{patterns}
        \draw [thick] (0.25,1) -- (0.25,2.5);
        \draw[-] (-0.5,0.25) -- (3,0.25);
        \draw[-] (1,-0.25) -- (1,3);
        \fill[white] (1,0.25) circle (2pt);
        \draw (1,0.25) circle (2pt);
        \draw (1,0.25) node[anchor=south west] {\tiny $O$};
        \fill (0.25,1) circle (2pt);
        \draw (0.25,1) node[anchor=east] {\tiny$B$};
        \fill (0.25,2.5) circle (2pt);
        \draw (0.25,2.5) node[anchor=east] {\tiny$C$};
        \draw (1.27,-.6) node[anchor=north] {\footnotesize (3) $a_2\le0<a_1$};
      \end{scope}
      %(4)
      \begin{scope}[shift={(0,0)}]
        \usetikzlibrary{patterns}
        \fill[black!10] (0,3)--(1.5,1.5)--(1.5,0)--(0,0)--(0,3);
        \draw[thick] (0,3)--(1.5,1.5)--(1.5,0)--(0,0)--(0,3);
        \draw[dashed,thick](0,3)--(2.15,1.25) (2.15,1.15)--(1.5,0);
        \draw[-] (-0.5,1.2) -- (3.5,1.2);
        \draw[-] (2.2,-0.25) -- (2.2,3.5);
        \fill[white] (2.2,1.2) circle (2pt);
        \draw (2.2,1.2) circle (2pt);
        \draw (2.2,1.2) node[anchor=north west] {\tiny$O$};
        \fill (1.5,0) circle (2pt);
        \draw (1.5,0) node[anchor=west] {\tiny$A$};
        \fill (0,0) circle (2pt);
        \draw (0,0) node[anchor=east] {\tiny$B$};
        \fill (0,3) circle (2pt);
        \draw (0,3) node[anchor=east] {\tiny$C$};
        \fill (1.5,1.5) circle (2pt);
        \draw (1.5,1.5) node[anchor=east] {\tiny$D_1$};
        \draw (1.37,-0.5) node[anchor=north] {\footnotesize (4) $0<ba_2\leq a_1$};
      \end{scope}
      %(5)
      \begin{scope}[shift={(5.5,0)}]
        \usetikzlibrary{patterns}
        \fill[black!10] (3,0)--(1.3,1)--(0,1)--(0,0)--(3,0);
        \draw[thick] (3,0)--(1.3,1)--(0,1)--(0,0)--(3,0);
        \draw[dashed,thick](3,0)--(0.75,1.75)--(0,1);
        \draw[-] (-0.5,1.75) -- (3.5,1.75);
        \draw[-] (0.75,-0.25) -- (0.75,3.5);
        \fill[white] (0.75,1.75) circle (2pt);
        \draw (0.75,1.75) circle (2pt);
        \draw (0.75,1.75) node[anchor=south west] {\tiny$O$};
        \fill (3,0) circle (2pt);
        \draw (3,0) node[anchor=west] {\tiny$A$};
        \fill (0,0) circle (2pt);
        \draw (0,0) node[anchor=east] {\tiny$B$};
        \fill (0,1) circle (2pt);
        \draw (0,1) node[anchor=east] {\tiny$C$};
        \fill (1.3,1) circle (2pt);
        \draw (1.3,1) node[anchor=north] {\tiny$D_2$};
        \draw (1.37,-.5) node[anchor=north] {\footnotesize (5) $0<ca_1\leq a_2$};
      \end{scope}
      %(6)
      \begin{scope}[shift={(0,-5.5)}]
        \usetikzlibrary{patterns}
        \fill[black!10]  (0,3)--(1.5,2.3)--(2,0)--(0,0)--(0,3);
        \draw[thick] (0,3)--(0,0)--(2,0); 
        \draw[dashed,thick] (0,3)--(1.5,2.3)--(2,0);
        \draw[-] (-0.5,2.3) -- (3.5,2.3);
        \draw[-] (1.5,-0.25) -- (1.5,3.5);
        \fill[white] (1.5,2.3) circle (2pt);
        \draw (1.5,2.3) circle (2pt);
        \draw (1.5,2.3) node[anchor=south west] {\tiny$O$};
        \fill (2,0) circle (2pt);
        \draw (2,0) node[anchor=west] {\tiny$A$};
        \fill (0,0) circle (2pt);
        \draw (0,0) node[anchor=east] {\tiny$B$};
        \fill (0,3) circle (2pt);
        \draw (0,3) node[anchor=east] {\tiny$C$};
        \draw (1.42,-.5) node[anchor=north] {\footnotesize (6) $0<a_1<ba_2$,};
        \draw (1.46,-1) node[anchor=north] {\footnotesize \hspace{10pt} $0<a_2<ca_1$,};
        \draw (1.17,-1.5) node[anchor=north] {\footnotesize \hspace{10pt} \tiny{$(a_1,a_2):$ non-imaginary root}};
      \end{scope}
      %(6')
      \begin{scope}[shift={(5.5,-5.5)}]
        \usetikzlibrary{patterns}
        \fill[black!10]  (0,3)--(1,0.5)--(2.25,0)--(0,0)--(0,3);
        \draw[thick] (0,3)--(0,0)--(2.25,0);
        \draw[dashed,thick] (0,3)--(1,0.5)--(2.25,0);
        \draw[-] (-0.5,0.5) -- (3.5,0.5);
        \draw[-] (1,-0.25) -- (1,3.5);
        \fill[white] (1,0.5) circle (2pt);
        \draw (1,0.5) circle (2pt);
        \draw (1,0.5) node[anchor=south west] {\tiny$O$};
        \fill (2.25,0) circle (2pt);
        \draw (2.25,0) node[anchor=west] {\tiny$A$};
        \fill (0,0) circle (2pt);
        \draw (0,0) node[anchor=east] {\tiny$B$};
        \fill (0,3) circle (2pt);
        \draw (0,3) node[anchor=east] {\tiny$C$};
        \draw (1.47,-.5) node[anchor=north] {\footnotesize (6) $0<a_1<ba_2$,};
        \draw (1.51,-1) node[anchor=north] {\footnotesize \hspace{10pt} $0<a_2<ca_1$,};
        \draw (1.27,-1.5) node[anchor=north] {\footnotesize \hspace{10pt} \tiny{$(a_1,a_2):$ imaginary root}};
      \end{scope}
    \end{tikzpicture}
    \caption{Consider the points $O=(0,0)$, $A=(-a_1+ba_2,-a_2)$, $B=(-a_1,-a_2)$, $C=(-a_1,-a_2+ca_1)$, $D_1=(-a_1+ba_{2},ca_{1}-(bc+1)a_{2})$, and $D_2=(ba_{2}-(bc+1)a_{1},-a_2+ca_{1})$.  Then the support region of $x[a_1,a_2]$ can be visualized as above.} 
    \label{fig:greedy polytopes}
  \end{figure}

>>>>

  When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
  We will therefore assume that $bc\ge4$.
  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$, $a_1,a_2\in\ZZ$, inside its \emph{dominance polygon} $\cP(\lambda)$.
  %In this case, we compute the possible transitions between any two pointed bases.
  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
  \begin{theorem}
    \label{th:dominance inequalities}
    The dominance polygon $\cP(\lambda)$ pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
    {
      \everymath={\displaystyle}
      \def\arraystretch{2.8}
      \[
        \begin{array}{rcccl}
          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
          \\
          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
          \\
          0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
          \\
          \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
        \end{array}
      \]
    }
  \end{theorem}

  A number of bases for rank two cluster algebras with various defining properties have been constructed.
  A natural starting basis is the so-called \emph{greedy basis} in which all $c^\lambda_{a_1,a_2}$ are non-negative and these coefficients are chosen to be minimal.
  It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications with the subalgebras of $\ZZ[x_1^{\pm1},x_2^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
  However, these bases depend on $k$ and the triangular basis is defined by a triangular transition with the stipulation that the basis does not depend on the choice of starting cluster.
  It would be useful to explicitly (or combinatorially) compute the transitions between these bases.
  However, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.

@@

\begin{figure}[h!]
  \centering
    \newcommand{\boundingrays}{
      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
      \draw [color=lightgray, thick, dashed] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
    }
  \begin{tikzpicture}[scale=.3]
    \begin{scope}[shift={(0,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l,\l) circle (6pt);
    \end{scope}
    \begin{scope}[shift={(13,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l *\b + \l, - \l) circle (6pt);
      \draw [very thick, join=round] (\l * \b + \l, -\l) -- (\l,-\l);
    \end{scope}
    \begin{scope}[shift={(26,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, \l) circle (6pt);
      \draw [very thick, join=round] (-\l, \l) -- (-\l,\l + \l*\c);
    \end{scope}
    \begin{scope}[shift={(39, 0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, -\l) circle (6pt);
      \draw [very thick, join=round] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
    \end{scope}
    \begin{scope}[shift={(0,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c -0.1; \y = -\l; }
      \fill (\x,\y) circle (6pt);
      \draw [very thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
    \end{scope}
    \begin{scope}[shift={(13,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c + 0.15; \y = -\l - 3*\l/10;}
      \fill (\x,\y) circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dash dot] (0,0);
      \draw [very thick, dash dot, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(26,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
      \fill (\x,\y) circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dash dot] (0,0);
      \draw [very thick, dash dot, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(39,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \c*\l/\b/1.03; \y = -\l; }
      \fill (\x , \y)  circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);
      \draw [very thick, dashed, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
      \draw [very thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
    \end{scope}
  \end{tikzpicture}
\end{figure}

@@

  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
    For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
    \begin{enumerate}
      \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
      \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
      \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
      \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
      \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
      \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
      $$\aligned
      R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
      &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
      &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
      \endaligned
      $$
    \end{enumerate}
    Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$. 
  \end{theorem}
